---
title: "Preparation"
format: 
  html:
    code-fold: false
    code-tools: false
editor: source
---


Here are some preparation information for the participants.

## Software

In this workshop we will be using R. You can either

-   have **R and Rstudio** installed on your laptop
-   or, use **Posit cloud** (formerly Rstudio Cloud).

[Posit cloud](https://posit.cloud) is free of charge for personal users, yet you need to [sign up](https://posit.cloud/plans/free) for a new user account and have internet connection.

## Install Bioconductor
 
```{r}
#| eval: false
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install(version = "3.17")
```

## Install Bioconductor Packages
```{r}
#| eval: false
BiocManager::install(c("TCGAbiolinks", "SummarizedExperiment", "maftools"))
```

## Data

The datasets we use can be found here Genomic Data Commons (GDC): <https://gdc.cancer.gov/>.

## Code

The R scripts used in part 1 and part 2 can be found here <https://github.com/omicscenter/TCGADataAnalysiswithR>.

